Measuring Perceptions and Preferences for Meritocracy

### 2021-07-08 paper_study1.Rmd
instructions
- mayor detalle de instrucciones dentro de chunks

```{r table-issp, echo=FALSE}
pacman::p_load(knitr, kableExtra, dplyr)
table_format = if(knitr::is_html_output()) {
  "html"
} else if(knitr::is_latex_output()) {
  "latex"
}

fsize = if(knitr::is_html_output()) {
  20
} else if(knitr::is_latex_output()) {
  12
}

tableissp <- read.csv(file = "input/tables/table-issp.csv",header = 1,sep = ";",encoding = "UTF-8") # call file generated externally for the table
cnames <- c("Component", "Dimensions","Item")
cap <- "Items of the ISSP meritocratic perceptions and preferences measures"

@@

```{r desc-issp, eval=FALSE, include=FALSE, results='asis'}
load(file = "input/data/proc/data_s1.RData")
pacman::p_load(dplyr)
table_format = if(knitr::is_html_output()) {
  "html"
} else if(knitr::is_latex_output()) {
  "latex"
}

table_format2 = if(knitr::is_html_output()) {
  T
} else if(knitr::is_latex_output()) {
  F
}

@@

```{r}
load(file = "input/data/proc/data_s1.RData")
pacman::p_load(dplyr)
likert_issp<- data_s1 %>% 
  dplyr::select(hwork,ambition,wealthy,pareduc,
                race,gender,people,polcone,
                welljob,hardjob,family,child) %>% na.omit()

likert_issp <- sjlabelled::set_label(likert_issp,
                                     label = c("Hard work",
                                               "Having ambition",
                                               "Wealthy family",
                                               "Educated parents",
                                               "Race",
                                               "Gender",
                                               "Knowing people",
                                               "Political connections",
                                               "Well job",
                                               "Hard job",
                                               "Support family",
                                               "Has children"))

likert_issp <- sjmisc::rec(likert_issp, rec="rev", append=FALSE)
likert_issp <- 
  sjlabelled::set_labels(likert_issp,
                         labels = c("Essential","Very important","Fairly important",
                                    "Not very important","Not important at all"))

ggplot2::theme_set(ggplot2::theme(panel.background = ggplot2::element_rect(fill = "gray85",
                                                                           colour = "gray85"),
                                  panel.border = ggplot2::element_blank(),
                                  axis.text.y = ggplot2::element_text(size = 13,
                                                                      hjust = 1),
                                  title = ggplot2::element_text(size = 13,
                                                                face = "bold"),
                                  legend.text = ggplot2::element_text(size = 12),
                                  plot.caption = ggplot2::element_text(size = 10,
                                                                       face = "plain",
                                                                       hjust = 1)))
p1<- likert_issp %>%
  dplyr::select(hwork_r:ambition_r) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Perception meritocratic",
                        geom.size = c(0.62),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE) + 
  ggplot2::theme(legend.position = "none")

p2<-likert_issp %>%
  dplyr::select(wealthy_r:polcone_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Perception Non-meritocratic",
                        geom.size = c(0.9),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE)  + 
  ggplot2::theme(legend.position = "none")

p3<-likert_issp %>% 
  dplyr::select(welljob_r:hardjob_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Preference meritocratic",
                        geom.size = c(0.62),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE) + 
  ggplot2::theme(legend.position = "none")

p4<-likert_issp %>% 
  dplyr::select(family_r:child_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Preference Non-meritocratic",
                        geom.size = c(0.62),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE) +
  ggplot2::theme(legend.position = "none")

leg<- ggpubr::as_ggplot(
  ggpubr::get_legend(
    dplyr::select(likert_issp, family_r:child_r) %>%
      sjPlot::plot_likert(geom.colors = "PuBu", catcount = 5) +
      ggplot2::scale_fill_brewer(
        breaks = c(5:1),
        direction = -1,
        labels = c("Not important at all","Not very important","Fairly important",
                   "Very important","Essential")) +
      ggplot2::theme(legend.position = "bottom")
    )
  )
```

```{r likert-issp,fig.height=11,fig.width=11,fig.cap="Distribution of responses in the ISSP meritocracy items"}
cowplot::add_sub(
  cowplot::plot_grid(p1,p2,p3,p4,leg,
    align = "hv",
    axis = "a",
    nrow = 5,
    ncol = 1,
    rel_heights = c(1,2,1,1,0.25)
    ),
  label = paste0(
    "Source: Authors calculation based on International Social Survey Programme - Social Inequality 2009",
    " (n=",dim(likert_issp)[1],")"
    ),
  size = 10,
  hjust = 0.25
  ) %>% 
  cowplot::ggdraw() 
```

@@

```{r corr-issp,fig.cap = "Perceptions and preferences for ISSP meritocracy items polychoric correlations", fig.align='center',fig.height=6,fig.width=8}
load(file = "input/data/proc/data_s1.RData")
pacman::p_load(dplyr)
cor_issp<- 
  data_s1 %>%
  dplyr::select(hwork,ambition,wealthy,pareduc,
                race,gender,people,polcone,
                welljob,hardjob,family,child) %>% 
  lavaan::lavCor(., ordered=names(.))
diag(cor_issp) = NA
rownames(cor_issp) <- c("A. Hard work",
                       "B. Having ambition",
                       "C. Wealthy family",
                       "D. Educated parents",
                       "E. Race",
                       "F. Gender",
                       "G. Knowing people",
                       "H. Political connections",
                       "I. Well job",
                       "J. Hard job",
                       "K. Support family",
                       "L. Has children")
colnames(cor_issp) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)", 
                       "(H)", "(I)","(J)","(K)","(L)")
corrplot::corrplot(cor_issp,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  lower.col = "black")
```

@@

```{r sum-fit-issp}
load(file = "input/data/proc/data_s1.RData")
pacman::p_load(dplyr, kableExtra, knitr)

table_format = if(knitr::is_html_output()) {
  "html"
} else if(knitr::is_latex_output()) {
  "latex"
}

table_format2 = if(knitr::is_html_output()) {
  T
} else if(knitr::is_latex_output()) {
  F
}

fsize = if(knitr::is_html_output()) {
  20
} else if(knitr::is_latex_output()) {
  12
}

cfa_perpref1 <- '
	  # latent variables
	  percmerit =~ hwork + ambition
	  percnmerit=~ wealthy + pareduc +race + gender +people + polcone
	  prefmerit =~ welljob + hardjob
	  prefnmerit=~ family + child
	  '
fit_perpref1 <- lavaan::cfa(cfa_perpref1, data = data_s1,ordered = T)

cfa_perpref2 <- '
	  # latent variables
	  percmerit =~ hwork + ambition
	  parents =~ wealthy + pareduc
	  backgrd =~ race + gender
	  networks=~ people + polcone
	  percnmerit=~ parents + backgrd + networks
	  prefmerit =~ welljob + hardjob
	  prefnmerit=~ family + child
	  '
fit_perpref2 <- lavaan::cfa(cfa_perpref2, data = data_s1,ordered = T)

@@

```{r tb-perpref1, echo=FALSE}
load(file = "input/data/proc/data_s1.RData")
pacman::p_load(dplyr,knitr,kableExtra)
options(knitr.kable.NA = '')
table_format = if(knitr::is_html_output()) {
  "html"
} else if(knitr::is_latex_output()) {
  "latex"
}

table_format2 = if(knitr::is_html_output()) {
  T
} else if(knitr::is_latex_output()) {
  F
}

cfa_perpref1 <- '
	  # latent variables
	  percmerit =~ hwork + ambition
	  percnmerit=~ wealthy + pareduc +race + gender +people + polcone
	  prefmerit =~ welljob + hardjob
	  prefnmerit=~ family + child
	  '
fit_perpref1 <- lavaan::cfa(cfa_perpref1, data = data_s1,
                            ordered = c("wealthy","pareduc","ambition","hwork",
                                        "people","polcone","race","gender",
                                        "respons","yeduc",
                                        "family","child",
                                        "welljob","hardjob"))
labs <- c(
  "Importance: hard work",
  "Importance: having ambition",
  "Importance: wealthy family",
  "Importance: educated parents",
  "Importance: race",
  "Importance: gender",
  "Importance: knowing people",
  "Importance: political connections",
  "Reasons for pay: well job",
  "Reasons for pay: hard job",
  "Reasons for pay: support family",
  "Reasons for pay: has children"
)

tb.load<- data.frame(round(cbind(lavaan::inspect(fit_perpref1,
                                                        what="std")$lambda),
                           digits = 3))
tb.load[tb.load==c(0.00)] <- NA

for (i in names(tb.load)) {
  tb.load[,i] <- sprintf(tb.load[,i], fmt = '%#.3f')
}
tb.load[tb.load=="NA"] <- ""
#-------#
fm01<- data.frame(t(data.frame(lavaan::fitmeasures(fit_perpref1, output ="matrix")[c("chisq","df","cfi","tli","rmsea"),]))); row.names(fm01) ="percnmerit"

#------chi2, df------#
fm04<- round(rbind(fm01),3)
fm04.1 <- fm04 %>% dplyr::select(chisq,df) 
fm04.1$chisq <- round(x = fm04.1$chisq,digits = 1)
fm04.1$df <- round(x = fm04.1$df,digits = 0)
fm04.1$chi2df <- paste0(fm04.1$chisq,"(",fm04.1$df,")")
fm04.1 <- dplyr::select(fm04.1,"chi2df")
for (i in names(fm04.1)) {
  fm04.1[,i] <- as.character(fm04.1[,i])
}

#------CFI, RMSEA------#
fm04.2 <- fm04 %>% dplyr::select(cfi,tli,rmsea) 
for (i in names(fm04.2)) {
  fm04.2[,i] <- sprintf(fm04.2[,i], fmt = '%#.3f')
}

fm.df      <- dplyr::bind_cols(fm04.1,fm04.2)
fm.df$nobs <- c(lavaan::nobs(fit_perpref1)) 
fm.df <- data.frame(t(fm.df)); colnames(fm.df) <- c("percnmerit")

#------ merge ------#
tb.fm<- dplyr::bind_rows(tb.load,fm.df)
tb.fm<- tb.fm %>% 
  dplyr::mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$",
                       "$\\text{TLI}$","$\\text{RMSEA}$","$N$")) %>%
  dplyr::select(vars,everything())
tb.perpref1 <- tb.fm

>>>>

```{r table-issp, echo=FALSE}
pacman::p_load(knitr, kableExtra, dplyr)
table_format = if(knitr::is_html_output()) { #conditional instructions for kable
  "html" #if html set "html" in format
} else if(knitr::is_latex_output()) {
  "latex"#if latex set "latex" in format
}

fsize = if(knitr::is_html_output()) { #conditional instructions for kable
  20 # if html set table fontsize to 20
} else if(knitr::is_latex_output()) {
  12 # if latex set table fontsize to 12
}

tableissp <- read.csv(file = "input/tables/table-issp.csv",header = 1,sep = ";",encoding = "UTF-8") # call file generated externally for the table
cnames <- c("Component", "Dimensions","Item") # table column names
cap <- "Items of the ISSP meritocratic perceptions and preferences measures" # Table caption

@@

```{r desc-issp, eval=FALSE, include=FALSE, results='asis'}
load(file = "input/data/proc/data_s1.RData")
pacman::p_load(dplyr)
table_format = if(knitr::is_html_output()) { #conditional instructions for kable
  "html" #if html set "html" in format
} else if(knitr::is_latex_output()) {
  "latex"#if latex set "latex" in format
}

fsize = if(knitr::is_html_output()) { #conditional instructions for kable
  20 # if html set table fontsize to 20
} else if(knitr::is_latex_output()) {
  12 # if latex set table fontsize to 12
}

@@

```{r}
load(file = "input/data/proc/data_s1.RData")
pacman::p_load(dplyr)
likert_issp<- data_s1 %>% 
  dplyr::select(hwork,ambition,wealthy,pareduc,
                race,gender,people,polcone,
                welljob,hardjob,family,child) %>% na.omit() #Subset variables
# Set labels for each variable
likert_issp <- sjlabelled::set_label(likert_issp,
                                     label = c("Hard work",
                                               "Having ambition",
                                               "Wealthy family",
                                               "Educated parents",
                                               "Race",
                                               "Gender",
                                               "Knowing people",
                                               "Political connections",
                                               "Well job",
                                               "Hard job",
                                               "Support family",
                                               "Has children")) 
#Reverse coding (ONLY) for plot
likert_issp <- sjmisc::rec(likert_issp, rec="rev", append=FALSE)
#Set value labels for plot
likert_issp <- 
  sjlabelled::set_labels(likert_issp,
                         labels = c("Essential","Very important","Fairly important",
                                    "Not very important","Not important at all"))

# Declare ggplot2 features
ggplot2::theme_set(ggplot2::theme(panel.background = ggplot2::element_rect(fill = "gray85",
                                                                           colour = "gray85"),
                                  panel.border = ggplot2::element_blank(),
                                  axis.text.y = ggplot2::element_text(size = 13,
                                                                      hjust = 1),
                                  title = ggplot2::element_text(size = 13,
                                                                face = "bold"),
                                  legend.text = ggplot2::element_text(size = 12),
                                  plot.caption = ggplot2::element_text(size = 10,
                                                                       face = "plain",
                                                                       hjust = 1)))
#Plot 1: Perception meritocratic
p1<- likert_issp %>%
  dplyr::select(hwork_r:ambition_r) %>%
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Perception meritocratic",
                        geom.size = c(0.62),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE) + 
  ggplot2::theme(legend.position = "none") 
#Plot 2: Perception Non-meritocratic
p2<-likert_issp %>%
  dplyr::select(wealthy_r:polcone_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Perception Non-meritocratic",
                        geom.size = c(0.9),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE)  + 
  ggplot2::theme(legend.position = "none")
#Plot 3: Preference meritocratic
p3<-likert_issp %>% 
  dplyr::select(welljob_r:hardjob_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Preference meritocratic",
                        geom.size = c(0.62),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE) + 
  ggplot2::theme(legend.position = "none")
#Plot 4: Preference Non-meritocratic
p4<-likert_issp %>% 
  dplyr::select(family_r:child_r) %>% 
  sjPlot::plot_likert(geom.colors = "PuBu",
                      title = "Preference Non-meritocratic",
                        geom.size = c(0.62),
                        catcount = 5,
                        expand.grid = T,
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE) +
  ggplot2::theme(legend.position = "none")

#Legend: Extract legend for the final plot using ggpubr
leg<- ggpubr::as_ggplot(
  ggpubr::get_legend(
    dplyr::select(likert_issp, family_r:child_r) %>%
      sjPlot::plot_likert(geom.colors = "PuBu", catcount = 5) +
      ggplot2::scale_fill_brewer(
        breaks = c(5:1),
        direction = -1,
        labels = c("Not important at all","Not very important","Fairly important",
                   "Very important","Essential")) +
      ggplot2::theme(legend.position = "bottom")
    )
  )
```

```{r likert-issp,fig.height=11,fig.width=11,fig.cap="Distribution of responses in the ISSP meritocracy items"}
#Final plot
cowplot::add_sub(
  cowplot::plot_grid(p1,p2,p3,p4,leg, #plot 1,2,3,4 and legend (bottom)
    align = "hv",
    axis = "a",
    nrow = 5, #5 plots
    ncol = 1, #1 column
    rel_heights = c(1,2,1,1,0.25) #fig size within plot
    ),
  label = paste0(
    "Source: Authors calculation based on International Social Survey Programme - Social Inequality 2009",
    " (n=",dim(likert_issp)[1],")"
    ),        # Caption: source and sample size 
  size = 10,  # Caption font size
  hjust = 0.25# Caption align 
  ) %>% 
  cowplot::ggdraw() 
```

@@

```{r corr-issp,fig.cap = "Perceptions and preferences for ISSP meritocracy items polychoric correlations", fig.align='center',fig.height=6,fig.width=8}
load(file = "input/data/proc/data_s1.RData")
pacman::p_load(dplyr)
# create polychoric correlation matrix
cor_issp<- 
  data_s1 %>%
  dplyr::select(hwork,ambition,wealthy,pareduc,
                race,gender,people,polcone,
                welljob,hardjob,family,child) %>% 
  lavaan::lavCor(., ordered=names(.)) 
diag(cor_issp) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_issp) <- c("A. Hard work", 
                       "B. Having ambition",
                       "C. Wealthy family",
                       "D. Educated parents",
                       "E. Race",
                       "F. Gender",
                       "G. Knowing people",
                       "H. Political connections",
                       "I. Well job",
                       "J. Hard job",
                       "K. Support family",
                       "L. Has children")
#set Column names of the matrix
colnames(cor_issp) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)", 
                       "(H)", "(I)","(J)","(K)","(L)")

#Plot the matrix using corrplot
corrplot::corrplot(cor_issp,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-",
  lower.col = "black")
```

@@

```{r sum-fit-issp}
load(file = "input/data/proc/data_s1.RData")
pacman::p_load(dplyr, kableExtra, knitr)
table_format = if(knitr::is_html_output()) { #conditional instructions for kable
  "html" #if html set "html" in format
} else if(knitr::is_latex_output()) {
  "latex"#if latex set "latex" in format
}

fsize = if(knitr::is_html_output()) { #conditional instructions for kable
  20 # if html set table fontsize to 20
} else if(knitr::is_latex_output()) {
  12 # if latex set table fontsize to 12
}
# meassurement model: First order 
cfa_perpref1 <- ' 
	  # latent variables
	  percmerit =~ hwork + ambition
	  percnmerit=~ wealthy + pareduc +race + gender +people + polcone
	  prefmerit =~ welljob + hardjob
	  prefnmerit=~ family + child
	  '
# Model fit: First order 
fit_perpref1 <- lavaan::cfa(cfa_perpref1, data = data_s1,ordered = T)

# meassurement model: Second order 
cfa_perpref2 <- '
	  # latent variables
	  percmerit =~ hwork + ambition
	  parents =~ wealthy + pareduc
	  backgrd =~ race + gender
	  networks=~ people + polcone
	  percnmerit=~ parents + backgrd + networks
	  prefmerit =~ welljob + hardjob
	  prefnmerit=~ family + child
	  '
# Model fit: second order 
fit_perpref2 <- lavaan::cfa(cfa_perpref2, data = data_s1,ordered = T)

@@

```{r tb-perpref1, echo=FALSE}
load(file = "input/data/proc/data_s1.RData")
pacman::p_load(dplyr,knitr,kableExtra)
options(knitr.kable.NA = '')
table_format = if(knitr::is_html_output()) { #conditional instructions for kable
  "html" #if html set "html" in format
} else if(knitr::is_latex_output()) {
  "latex"#if latex set "latex" in format
}

fsize = if(knitr::is_html_output()) { #conditional instructions for kable
  20 # if html set table fontsize to 20
} else if(knitr::is_latex_output()) {
  12 # if latex set table fontsize to 12
}

# First order model for Appendix
cfa_perpref1 <- '
	  # latent variables
	  percmerit =~ hwork + ambition
	  percnmerit=~ wealthy + pareduc +race + gender +people + polcone
	  prefmerit =~ welljob + hardjob
	  prefnmerit=~ family + child
	  '
# Fit First order model for Appendix
fit_perpref1 <- lavaan::cfa(cfa_perpref1, data = data_s1,
                            ordered = c("wealthy","pareduc","ambition","hwork",
                                        "people","polcone","race","gender",
                                        "respons","yeduc",
                                        "family","child",
                                        "welljob","hardjob"))
# Labels of First order model for Appendix
labs <- c(
  "Importance: hard work",
  "Importance: having ambition",
  "Importance: wealthy family",
  "Importance: educated parents",
  "Importance: race",
  "Importance: gender",
  "Importance: knowing people",
  "Importance: political connections",
  "Reasons for pay: well job",
  "Reasons for pay: hard job",
  "Reasons for pay: support family",
  "Reasons for pay: has children"
)
#Extract factor loadings
tb.load<- data.frame(round(cbind(lavaan::inspect(fit_perpref1,
                                                        what="std")$lambda),
                           digits = 3))
tb.load[tb.load==c(0.00)] <- NA #set to NA factor loadings of 0

for (i in names(tb.load)) {
  tb.load[,i] <- sprintf(tb.load[,i], fmt = '%#.3f') #set values as character
}
tb.load[tb.load=="NA"] <- "" #set NA values to "" (empty space)
#---extract fit measures-------#
fm01<- data.frame(t(data.frame(lavaan::fitmeasures(fit_perpref1, output ="matrix")[c("chisq","df","cfi","tli","rmsea"),]))); row.names(fm01) ="percnmerit"

#------chi2, df------#
fm04<- round(rbind(fm01),3) #select and round to 4 digits
fm04.1 <- fm04 %>% dplyr::select(chisq,df) #select chi2 and degrees of freedom
fm04.1$chisq <- round(x = fm04.1$chisq,digits = 1) # round Chi2 to 1 digit
fm04.1$df <- round(x = fm04.1$df,digits = 0) #round Df to 0 digits
fm04.1$chi2df <- paste0(fm04.1$chisq,"(",fm04.1$df,")") #Paste chi2(df)
fm04.1 <- dplyr::select(fm04.1,"chi2df") #select final column
for (i in names(fm04.1)) {
  fm04.1[,i] <- as.character(fm04.1[,i]) # transform all to character
}

#------CFI, RMSEA------#
fm04.2 <- fm04 %>% dplyr::select(cfi,tli,rmsea) # select CFI, TLI and RMSEA
for (i in names(fm04.2)) {                      # transform all to character
  fm04.2[,i] <- sprintf(fm04.2[,i], fmt = '%#.3f')
}

fm.df      <- dplyr::bind_cols(fm04.1,fm04.2) # factor loading and labels
fm.df$nobs <- c(lavaan::nobs(fit_perpref1))   # add number of observations
fm.df <- data.frame(t(fm.df)); colnames(fm.df) <- c("percnmerit") #transpose and set colnames

#------ merge ------#
tb.fm<- dplyr::bind_rows(tb.load,fm.df) #merge factor loadings and fit indices
tb.fm<- tb.fm %>% 
  dplyr::mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$",
                       "$\\text{TLI}$","$\\text{RMSEA}$","$N$")) %>%
  dplyr::select(vars,everything()) #Change names of Fit meassures to latex symbols
tb.perpref1 <- tb.fm #final matrix for Table
